Title Goes Here

### 2024-05-13 analysis/paper/paper.qmd
EEO

library(googlesheets4)
library(stringi)
1

@@

EEO_word <- EEO_clean %>%
   unnest_tokens(word, text) %>%
  anti_join(get_stopwords()) %>%
  count(word, sort = TRUE)
```

```{r}
ggplot(word_data, aes(x = reorder(word, n), y = n)) +
  geom_col() +
  coord_flip() +  # Flips the axes for easier reading of text
  labs(x = "Words", y = "Frequency", title = "Word Frequency")
```

>>>>

@@

EEO_word <- EEO_clean %>%
   unnest_tokens(word, 
                 equal_employment_opportunity_statement) %>%
  anti_join(get_stopwords()) %>%
  count(word, sort = TRUE) %>%
  drop_na()

community_word <- c("women","color","religion","race","age","veteran","disability")

```{r}
ggplot(EEO_word, aes(x = reorder(word, n), y = n)) +
  geom_col() +
  coord_flip() +  
  labs(x = "Words", y = "Frequency", title = "Word Frequency")
```
